%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  System        : 
%  Module        : 
%  Object Name   : $RCSfile$
%  Revision      : $Revision$
%  Date          : $Date$
%  Author        : $Author$
%  Created By    : Robert Heller
%  Created       : Wed May 31 19:37:01 2017
%  Last Modified : <200210.1418>
%
%  Description 
%
%  Notes
%
%  History
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    Copyright (C) 2017  Robert Heller D/B/A Deepwoods Software
%			51 Locke Hill Road
%			Wendell, MA 01379-9728
%
%    This program is free software; you can redistribute it and/or modify
%    it under the terms of the GNU General Public License as published by
%    the Free Software Foundation; either version 2 of the License, or
%    (at your option) any later version.
%
%    This program is distributed in the hope that it will be useful,
%    but WITHOUT ANY WARRANTY; without even the implied warranty of
%    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%    GNU General Public License for more details.
%
%    You should have received a copy of the GNU General Public License
%    along with this program; if not, write to the Free Software
%    Foundation, Inc., 675 Mass Ave, Cambridge, MA 02139, USA.
%
% 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt,notitlepage,twoside]{book}
\usepackage{graphicx}
\usepackage{mathptm}
\usepackage{times}
\usepackage{makeidx}
\usepackage{ifpdf}
\ifpdf
\usepackage[pdftex,
            pagebackref=true,
            colorlinks=true,
            linkcolor=blue,
            unicode
           ]{hyperref}
\else
\usepackage[ps2pdf,
            pagebackref=true,
            colorlinks=true,
            linkcolor=blue,
            unicode
           ]{hyperref}
\usepackage{pspicture}
\fi
\usepackage{url}
\pagestyle{headings}
\makeindex
\emergencystretch=50pt
\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}
\includeonly{SMCSenseHAT,QuadSSSQuadIn,MCP23017,OctalLEDDriver,QuadSMCSenseHat,LCCCANCape,QuadSMCSenseCape,QuadSMCSenseHat,PocketBeagleQuadSMCSense,ESP32QuadSMCSense,ESP32-PWMHalfSiding}
\begin{document}
\title{Railroad Circuits for the Raspberry Pi, Beagle Bone Black, Pocket Beagle, and ESP32}
\author{Robert Heller \\ The Country Robot \\ Wendell, MA, USA}
\date{\today}
\begin{titlepage}

\maketitle

\clearpage

This documentation was prepared with \LaTeX.

\vspace{.25in}


{\small Copyright \copyright 2017-2019 by Robert Heller D/B/A The Country Robot}
\vspace{.25in}

All rights reserved.  Permission is granted to copy this document in
electronic form only, so long as it is with the software it
documents. 

\vspace{.125in}

The author, Robert Heller, may be contacted electronically (E-Mail) via
\url{mailto:heller@thecountryrobot.com}.

\vspace{.25in}

The Country Robot's web site URL: \url{http://www.thecountryrobot.com/}.

\thispagestyle{empty}
\setcounter{page}{0}
\clearpage

\end{titlepage}

\pagenumbering{roman}
\tableofcontents
\listoffigures
\listoftables
\cleardoublepage
\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

This booklet describes a collection of circuit boards I designed to make use 
of Raspberry Pi GPIO pins to be used in the control of a model railroad 
layout.  I am not formally trained as an electronics engineer, but these 
circuits are fairly simple and are readily cribbed from the data sheets of the 
various microchips used.  If someone who is a trained electronics engineer 
finds something wrong, I would of course like to hear about it.

\cleardoublepage
\pagenumbering{arabic}
\chapter{General Information}

Many of these boards are add on boards for a Raspberry Pi ``B'' model, 
one with a 40-pin header and have the mechanical form factor of a Raspberry Pi 
``HAT''.  Since none of them have an eeprom on them, they are technically not 
actual ``HATs''.  These boards can be ``stacked'', with some limitations, as 
indicated in their respective chapters, mainly because some of these boards 
are hard wired to use specific GPIO pins.  It is therefore possible to use 
``stacking'' (or ``stack through'') headers, headers that are both female 
sockets and male pins.  The end user has a choice of headers to use: standard 
female only headers, long female only headers, standard ``stacking'' headers 
or long/tall ``stacking'' headers.  In the chapters for each board in the 
parts list section, I list the various header options, with part numbers and 
suppliers.  Other boards are stackable ``Capes'' for the Beagle Bone Black. 
Again, since many of these boards are stackable, ``stacking'' (or ``stack 
through'') headers can be used.  Still other boards are for the Pocket Beagle 
and the ESP32 devkit board.  These latter are not meant to be stackable and 
for these, the add on board goes \textit{under} the processor board.  Unlike 
the Raspberry Pi and Beagle Bone Black, these smaller boards have no mounting 
holes, but the ``add on'' boards do.  Also for these smaller boards the add 
on boards provide power to the processor board.

Another place where the end user has choices is in the terminal blocks.  With 
some exceptions (mostly for higher power cases), all of the terminal blocks 
are specified as .1'' (2.54mm) pitch screw terminals.  It is possible to 
substitute other .1'' (2.54mm) pitch connections, including vertical or right 
angle pin arrays or even spring terminals.  This will depend on what sort of 
interconnection technology the end user would prefer.  In the parts list will 
be the various alternative options.

All of the boards use mostly through-hole parts and should be fairly easy to
hand solder with a basic good quality soldering iron. All of the components
are standard and readily available from various suppliers (like Mouser or
Digi-Key).

Most of the boards have mounting holes.  The mounting holes on the HAT-like 
boards align over the mounting holes in the Raspberry Pi.  Using standard 
height headers allows about 3/8'' between boards and using tall headers allows 
1/2'' between boards.  It is probably a good idea to use spacer hardware to 
secure the boards.  Male/female 4-40 threaded hex spacers work quite well, 
although the boards are designed to use M2.5 hardware (Adafruit sells M2.5 
male/female threaded hex spacers in pairs).

\include{SMCSenseHAT}
\include{QuadSSSQuadIn}
\include{MCP23017}
\include{OctalLEDDriver}
\include{LCCCANCape}
\include{QuadSMCSenseHat}
\include{QuadSMCSenseCape}
\include{PocketBeagleQuadSMCSense}
\include{ESP32QuadSMCSense}
\include{ESP32-PWMHalfSiding}
\cleardoublepage
%\bibliography{MRR}
%\bibliographystyle{plain}
\cleardoublepage
\printindex
\end{document}
